Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Add a subheading for the coclassification section of the results.
I expect to add more results before this section,
so separating it will be useful.
Add some additional numbers to the results section.

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.

@@

>>>>

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
The ungrouped model gave an AIC value of \aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.

@@

The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
The total Akaike weight assigned to models in which the rows and columns used the same grouping was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
